Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-11 programlogic.tex
+

\begin{figure*}
  \[
\begin{array}{l}
  \vaddr\mapsto_{\textsf{t}}\{\textsf{q}\}\vpage\; : \mathsf{vProp} \; \Sigma \;  \stackrel{{\triangle}}{:=} 
  \exists_{\entryf \;, \entrytr \;, \entrytw \;,\entryo} \ldotp

  \ulcorner \textsf{aligned } \vaddr \urcorner \ast  \\
 \quad \textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\rtv,\entryf,\entrytr,\entrytw,\entryo) \ast \nfpointsto{\mask\vaddr\ft\entryo}{\mask\vaddr\tw\entryo}\vpage\qfracone\naddr 
\end{array}
\]
\begin{lstlisting}[language=Coq]
 Definition L4_L1_PointsTo (cr3val maddr entry entry0 entry1 pte :word 64) : vProp $\Sigma$ :=
  ((l4M52 maddr cr3val) \$\sim$\ (l4off maddr cr3val) $\mapsto_{a}$ {q1} entry  $\ast$
  (l3M52 maddr entry) \$\sim$\ (l3off maddr entry)  $\mapsto_{a}$ {q2} entry0 $\ast$ 
  (l2M52 maddr entry0) \$\sim$\ (l2off maddr entry0) $\mapsto_{a}$ {q3} entry1 $\ast$
  (l1M52 maddr entry1) \$\sim$\ (l1off maddr entry1) $\mapsto_{a}$ {q4} pte ).
\end{lstlisting}
\caption{A Strong Virtual Points-to Relation}
\todo[inline,color=red]{Colin says: shouldn't that fraction be a q, not a 1, in the second line?}
  \label{fig:strongvirtualpointsto}
\end{figure*}

>>>>

\begin{figure*}
\begin{lstlisting}[language=Coq]
 Definition $\vaddr\mapsto_{\textsf{t}}\{\textsf{q}\}\vpage$ :vProp $\Sigma$ := 
  $\exists_{\entryf \;, \entrytr \;, \entrytw \;,\entryo} \ldotp$  $\ulcorner$ aligned $\vaddr \urcorner \ast$ L4_L1_PointsTo($\rtv,\entryf,\entrytr,\entrytw,\entryo$) $\ast \entryo \mapsto_{p} \vpage$.
 Definition L4_L1_PointsTo (rtv maddr entry entry0 entry1 pte :word 64) : vProp $\Sigma$ :=
  ((l4M52 maddr rtv) \$\sim$\ (l4off maddr rtv) $\mapsto_{a}$ {q1} entry  $\ast$
  (l3M52 maddr entry) \$\sim$\ (l3off maddr entry)  $\mapsto_{a}$ {q2} entry0 $\ast$ 
  (l2M52 maddr entry0) \$\sim$\ (l2off maddr entry0) $\mapsto_{a}$ {q3} entry1 $\ast$
  (l1M52 maddr entry1) \$\sim$\ (l1off maddr entry1) $\mapsto_{a}$ {q4} pte ).
\end{lstlisting}
\caption{A Strong Virtual Points-to Relation}
\todo[inline,color=red]{Colin says: shouldn't that fraction be a q, not a 1, in the second line?}
  \label{fig:strongvirtualpointsto}
\end{figure*}
